Designing a high-performance boundary element library with OpenCL and Numba

### 2021-05-28 final_submission/CISESI-2021-04-0035.R1_Betcke.tex
Added final files

\begin{figure}
	\centering
	\input{img/sphere}
	\caption{Discretization of a sphere into flat surface triangles.}
	\label{fig:triangulation}
\end{figure}

\begin{figure*}
	\centering
	\input{img/triangles}
	\caption{The four types of intersection of two triangles: the triangles can be (left to right) not neighbours, neighbours adjacent via a vertex, neighbours adjacent via an edge, or the same triangle. In the first case, standard quadrature is used. In the other three cases, singular quadrature rules must be used.}
	\label{fig:triangles}
\end{figure*}

@@

\begin{figure}
	\centering
	\input{img/bempp_overview}
	\caption{The layout of Bempp-cl with its computational backends.}
	\label{fig:overview}
\end{figure}

@@

\begin{figure*}
	\center
	\input{img/kernel_header}
	\caption{Definition of the OpenCL compute kernel for scalar integral equations.}
	\label{fig:kernel_definition}
\end{figure*}

@@

\begin{figure}
	\center
	\input{img/colouring}
	\caption{The triangles in this mesh have been colored (using a greedy algorithm) so that no two neighboring triangles are the same color. Sets of triangles of the same color can therefore be processed together as they are guaranteed to not be neighbors, so do not share any degrees of freedom. [The dots on each cell are included as a visual aid for anyone who prints this article in black and white.]}
	\label{fig:colouring}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=6cm]{img/intel_pocl_laplace_comp.pdf}
	\caption{Comparison of the performance of PoCL and the Intel OpenCL runtime for the assembly of the Laplace single-layer boundary operator on a grid with 32,768 elements.}
	\label{fig:intel_pocl_laplace_cmp}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=7cm]{img/pocl_single_layer.pdf}
	\caption{Comparison of the single-precision and double-precision performance for various grid sizes using PoCL and P0 basis functions.}
	\label{fig:pocl_single_layer}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=7cm]{img/efield_domain_potential.pdf}
	\caption{Evaluation of an electric field potential operator on CPU via PoCL vs Nvidia GPU}
	\label{fig:efield_domain_potential}
\end{figure}

>>>>

\begin{figure}
	\centering
	\input{sphere}
	\caption{Discretization of a sphere into flat surface triangles.}
	\label{fig:triangulation}
\end{figure}

\begin{figure*}
	\centering
	\input{triangles}
	\caption{The four types of intersection of two triangles: the triangles can be (left to right) not neighbours, neighbours adjacent via a vertex, neighbours adjacent via an edge, or the same triangle. In the first case, standard quadrature is used. In the other three cases, singular quadrature rules must be used.}
	\label{fig:triangles}
\end{figure*}

@@

\begin{figure}
	\centering
	\input{bempp_overview}
	\caption{The layout of Bempp-cl with its computational backends.}
	\label{fig:overview}
\end{figure}

@@

\begin{figure*}
	\center
	\input{kernel_header}
	\caption{Definition of the OpenCL compute kernel for scalar integral equations.}
	\label{fig:kernel_definition}
\end{figure*}

@@

\begin{figure}
	\center
	\input{colouring}
	\caption{The triangles in this mesh have been colored (using a greedy algorithm) so that no two neighboring triangles are the same color. Sets of triangles of the same color can therefore be processed together as they are guaranteed to not be neighbors, so do not share any degrees of freedom. [The dots on each cell are included as a visual aid for anyone who prints this article in black and white.]}
	\label{fig:colouring}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=6cm]{intel_pocl_laplace_comp.pdf}
	\caption{Comparison of the performance of PoCL and the Intel OpenCL runtime for the assembly of the Laplace single-layer boundary operator on a grid with 32,768 elements.}
	\label{fig:intel_pocl_laplace_cmp}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=7cm]{pocl_single_layer.pdf}
	\caption{Comparison of the single-precision and double-precision performance for various grid sizes using PoCL and P0 basis functions.}
	\label{fig:pocl_single_layer}
\end{figure}

@@

\begin{figure}
	\center
	\includegraphics[width=7cm]{efield_domain_potential.pdf}
	\caption{Evaluation of an electric field potential operator on CPU via PoCL vs Nvidia GPU}
	\label{fig:efield_domain_potential}
\end{figure}
